---
title: "GDPR Fines Tracker & Statistics"
author:  |
    [![Logo](https://mk0privacyaffaidetc8.kinstacdn.com/wp-content/uploads/2019/10/PrivacyAffairs-Logo-SVG.svg)](https://www.privacyaffairs.com/)
date: "Report Date: `r Sys.Date()`"
output:
  pagedown::html_paged:
    toc: false
    css: ["resources/css/custom-fonts.css", "resources/css/custom-page.css", "resources/css/custom.css"]
    # change to true for a self-contained document, but it'll be a litte slower for Pandoc to render
    self_contained: false
    .test: true
params:
  country: 
    label: "Country" 
    value: Poland
    input: select
    choices: [All, Austria, Belgium, Bulgaria, Croatia, Cyprus, Czech Republic, Denmark, France, Germany, Greece, Hungary, Iceland, Italy, Latvia, Lithuania, Malta, Netherlands, Norway, Poland, Portugal, Romania, Slovakia, Spain, Sweden, United Kingdom]
subtitle: '`r ifelse(params$country != "All", params$country, "All Countries")`'
# uncomment this line to produce HTML and PDF in RStudio:
#knit: pagedown::chrome_print
output_dir: "docs/"
output_file: "index.html"
---

```{r setup, include=FALSE}
library(dplyr)
library(tidyr)
library(purrr)
library(glue)
knitr::opts_chunk$set(echo = FALSE)

gdpr_violations <- readr::read_tsv('data/gdpr_violations.tsv')
gdpr_text <- readr::read_tsv('data/gdpr_text.tsv')

source("R/utils.R")

filtered_data <- create_df_filtered(gdpr_violations, params$country)

n_fines = nrow(filtered_data)
largest_fine = max(filtered_data$price)
largest_fine_controller = filtered_data$controller[filtered_data$price == largest_fine]
largest_fine_date = filtered_data$as_date[filtered_data$price == largest_fine]
largest_fine_country = filtered_data$name[filtered_data$price == largest_fine]

total_of_fines = sum(filtered_data$price)

smallest_fine = min(filtered_data$price[filtered_data$price > 0])
smallest_fine_controller = filtered_data$controller[filtered_data$price == smallest_fine]
smallest_fine_date = filtered_data$as_date[filtered_data$price == smallest_fine]
smallest_fine_country = filtered_data$name[filtered_data$price == smallest_fine]

recent_5 = top_n(filtered_data, 5, as_date) %>% select(date, controller, price) %>% mutate(price = pretty_num(price))
top_5 = arrange(top_n(filtered_data, 5, price), desc(price)) %>% select(picture, controller, price) %>% mutate(price = pretty_num(price), picture = sprintf("![](%s)", picture))
```

```{css}
a[href^="http"]:not([class="uri"])::after {
  content: "";
}
```

# {-}

<!-- https://bookdown.org/yihui/rmarkdown-cookbook/custom-blocks.html -->
::::: {.dashboard__wrapper}
:::: {.dashboard__wrapper--left}

::: {.head}
Total Number of GDPR Fines
:::
::: {.number}
`r n_fines`
:::

::: {.head}
Largest Fine
:::
::: {.number}
`r pretty_num(largest_fine)`
:::
::: {.subhead}
<span>`r largest_fine_controller`</span> on `r pretty_date(largest_fine_date)` - `r largest_fine_country`
::: 

::::
:::: {.dashboard__wrapper--right}

::: {.head}
Total Amount of GDPR Fines
:::
::: {.number}
`r pretty_num(total_of_fines)`
:::

::: {.head}
Smallest Fine
:::
::: {.number}
`r pretty_num(smallest_fine)`
:::
::: {.subhead}
<span>`r smallest_fine_controller`</span> on `r pretty_date(smallest_fine_date)` - `r smallest_fine_country`
:::

::::
:::::

::::: {.stats__wrapper}
:::: {.stats__wrapper--left}

::: {.head}
5 Most Recent GDPR Fines
:::
::: {.subhead}
*Only includes finalized cases
:::
::: {.data-recent}
`r knitr::kable(recent_5)` 
:::
::::

:::: {.stats__wrapper--right}
::: {.head}
Top 5 Biggest GDPR Fines
:::
::: {.subhead}
*Only includes final & binding fines
:::
::: {.data-fines}
`r knitr::kable(top_5, col.names = NULL, align = "llr")`
:::
::::

:::::

# Full list of all GDPR fines {-}

```{r, results='asis', echo = FALSE}

rmarkdown_text = create_text_filtered(gdpr_violations, params$country)

cat(rmarkdown_text, sep = '\n\n')
```
